Review questions list

### 2020-10-10 docs/revision/review.tex
update: revision list
update: review-list
* reply

\fix The names should be checked

@@

\fix Calculation is done AY will place values on graph.

@@

	\textcolor{darkgreen}{ANSWER: } We can safely drop this argument, or reframe in a way that we are not absolutely sure as more research is required on this topic. \textcolor{red}{Following CK comment: Will be reframed as to what we have seen.}

@@

\item \textbf{-MEDIUM-} Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref. [18] is also improved."- Following from the previous comments- if the comparison is not for the similar designs then you can't state this improvement. So please elaborate on this. \\
\textcolor{red}{Following CK comment: A fix added by HA, to be unfixed}

>>>>

\fix The names should be checked ... \fixed

\reply regarding the validation curves if we do not have space.

@@

\fix Calculation is done AY will place values on graph... \fixed

@@

	\textcolor{darkgreen}{ANSWER: } We can safely drop this argument, or reframe in a way that we are not absolutely sure as more research is required on this topic. \textcolor{red}{Following CK comment: Will be reframed as to what we have seen.} CK: I have removed the sentence as the explanation could have easily extended to 4-5 lines. In the reply we can talk about doing experiments about this. \fixed

@@

\textcolor{red}{CK: That is our claim. We are saying any random ANN cannot generalize to other planes, ours can. Also, in real life you don't have a dataset to design your ANN for. Optimizing an ANN for a single database is considered cheating as this never happens in reality.}

\item \textbf{-MEDIUM-} Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref. [18] is also improved."- Following from the previous comments- if the comparison is not for the similar designs then you can't state this improvement. So please elaborate on this. \\
\textcolor{red}{Following CK comment: A fix added by HA, to be unfixed}
\fixed{} We have to explain the problem in the reply.
